User-level Grid Monitoring with Inca 2

### 2007-02-22 pubs/papers/hpdc-gmw-2007/paper.tex
small commit to test email to cathie
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6541 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

An Inca reporter is an executable program that tests or measures some aspect
of a system or installed software.   Reporter executables are designed to be
easy to produce and can be run outside of the Inca system (e.g., by a system
administrator).  A reporter should be written following the user-level
monitoring guidelines described in the introduction and could be a simple
Globus~\cite{globus} GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
support certain command line options and produce an XML report according to
the Inca reporter schema.  The goal of the reporter schema is to accomodate
multiple types of data and to capture information about the the reporter
execution to diagnose any detected failures.  The reporter schema consists of
the following elements:

@@

We provide an extensible set of Perl APIs to handle much of the effort of
writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
pings a pre-WS Globus GRAM server and (b) its corresponding output when
executed on a local machine.  The reporter uses two of the Perl APIs:
Inca::Reporter::SimpleUnit (which is a subclass of Inca::Reporter) and
Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
functions for handling the required input arguments
(lines~\ref{pingReporter}(a) 12-14 $\rightarrow$ lines \ref{pingReporter}(b)
10-31) and printing the Inca-compliant header and exit status XML tags
(lines\ref{pingReporter}(a) 4-11, 24 $\rightarrow$ \ref{pingReporter}(b)
1-9,43-46).  It also includes some informational and debug logging functions
again similar to log4j; the log output has been very useful to system
administrators who can view a summary of the test or benchmark that the
reporter performed without reading the reporter source code.  Line
\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
executes a system command (using a 30 second timeout) and logs to the 'system'
level of the log XML output (lines \ref{pingReporter}(b) 32-36).  The subclass
Inca::Reporter::SimpleUnit is the API responsible for printing the simplist
standard reporter body schema -- reporting software functionality or service
tests results; it handles the printing of the small body XML
(lines~\ref{pingReporter}(b) 39-41) using the functions unitSuccesss
(line~\ref{pingReporter}(a) 22) or unitFailure (lines~\ref{pingReporter}(a)
18, 20) depending on the output of system command.  And finally, the
Inca::Reporter::GridProxy API (line~\ref{pingReporter}(a) 3) adds a proxy
dependency to the reporter which tells the Inca system to download a
short-term proxy before running this reporter (this is discussed further in
Section~\ref{proxy}).  Most current reporters use the Perl APIs and consist of
fewer than 30 lines of code.

@@

The Inca agent retrieves reporters from collections called reporter
repositories, that consist of reporters, required packages and libraries,
and a catalog file. Repository contents are accessible using a URL and can
be shared across multiple Inca deployments. The Inca team publishes a
reporter repository that contains reporters developed for TeraGrid.

>>>>

An Inca reporter is an executable program that tests or measures some aspect
of a system or installed software.   Reporter executables are designed to be
easy to produce and can be run outside of the Inca system (e.g., by a system
administrator).  A reporter should be written following the user-level
monitoring guidelines described in the introduction and could be a simple
Globus~\cite{globus} GRAM gatekeeper ping test (see Figure~\ref{pingReporter})
or a more complex Grid application benchmark~\cite{grasp}.  Reporters must
support certain command line options and produce an XML report according to
the Inca reporter schema.  The goal of the reporter schema is to accommodate
multiple types of data and to capture information about the reporter
execution to diagnose any detected failures.  The reporter schema consists of
the following elements:

@@

We provide an extensible set of Perl APIs to handle much of the effort of
writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
pings a pre-WS Globus GRAM server and (b) its corresponding output when
executed on a local machine.  The reporter uses two of the Perl APIs:
Inca::Reporter::SimpleUnit (which is a subclass of Inca::Reporter) and
Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
functions for handling the required input arguments
(lines~\ref{pingReporter}(a) 12-14 $\rightarrow$ lines \ref{pingReporter}(b)
10-31) and printing the Inca-compliant header and exit status XML tags
(lines\ref{pingReporter}(a) 4-11, 24 $\rightarrow$ \ref{pingReporter}(b)
1-9,43-46).  It also includes some informational and debug logging functions
again similar to log4j; the log output has been very useful to system
administrators who can view a summary of the test or benchmark that the
reporter performed without reading the reporter source code.  Line
\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
executes a system command (using a 30 second timeout) and logs to the 'system'
level of the log XML output (lines \ref{pingReporter}(b) 32-36).  The subclass
Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
standard reporter body schema -- reporting software functionality or service
tests results; it handles the printing of the small body XML
(lines~\ref{pingReporter}(b) 39-41) using the functions unitSuccesss
(line~\ref{pingReporter}(a) 22) or unitFailure (lines~\ref{pingReporter}(a)
18, 20) depending on the output of system command.  Finally, the
Inca::Reporter::GridProxy API (line~\ref{pingReporter}(a) 3) adds a proxy
dependency to the reporter telling the Inca system to download a
short-term proxy before running this reporter (this is discussed further in
Section~\ref{proxy}).  Most current reporters use the Perl APIs and consist of
fewer than 30 lines of code.

@@

The Inca agent retrieves reporters from collections called reporter
repositories that consist of reporters, required packages and libraries,
and a catalog file. Repository contents are accessible using a URL and can
be shared across multiple Inca deployments. The Inca team publishes a
reporter repository that contains reporters developed for TeraGrid.
